---
title: "Amazon Sales Profit Prediction"
execute: 
  echo: false
---

Sales profits from preferred sales channels have grown significantly. I gathered data from the Amazon Sales Kaggle dataset, covering 100 sales from 2010 to 2019. Using this information, we predicted future sales profits based on two main sales channels: Online and Offline. We modeled Total Profit, a numerical variable, as a linear function of Order Year. As the years progress, profits appear to increase. In conclusion, sales profits on both Sales Channel combined are predicted to rise by 764 unit each year with uncertainty varying from as low as 153.64% and as high as 307.29%. These rates are subject to external factors that could influence Amazon's profit margins.

```{r}
#| message: false
#| label: setup
#| warning: false

library(tidybayes)
library(tidyverse)
library(brms)
library(plotly)
```

```{r}
raw_df <- read_csv("data/AmazonSalesData.csv", show_col_types = FALSE)
```

```{r}
#| label: cleaning
#| message: false
#| warning: false
AmazonSales <- raw_df |>
  rename(`Manufacturing Cost` = `Unit Cost`,
         Total_Profit = `Total Profit`,
         Sales_Channel = `Sales Channel`) |>
  select(Sales_Channel, `Manufacturing Cost`, Total_Profit, `Order Priority`, `Order Date`, `Units Sold`) |> 
  mutate(`Order Priority` = recode(`Order Priority`,
                                   "H" = "High Priority",
                                   "C" = "Critical Priority",
                                   "L" = "Low Priority",
                                   "M" = "Medium Priority")) |>
  mutate(Order_Year = year(mdy(`Order Date`)))
```

```{r}
#| cache: true
#| message: false
#| label: brm_model
#| warning: false
fit_x2 <- brm(formula = Total_Profit ~ Order_Year + Sales_Channel,
              data = AmazonSales,
              family = gaussian(),
              silent = 2,
              refresh = 0,
              seed = 17)
```

```{r}
#| label: variable
#| message: false
#| warning: false
ndata = tibble("Order_Year" = c(2010:2017),
               "Sales_Channel" = rep(c("Online", "Offline"), times = 4))
```

```{r}
#| label: model
#| message: false
#| warning: FALSE

# Create a cool scatter plot
plot1 <- AmazonSales |>
  ggplot(aes(x = Total_Profit, y = `Units Sold`, color = Sales_Channel)) +
  geom_smooth(method = "lm", se = FALSE, linetype = "dashed", formula = y ~ x) + 
  scale_x_continuous(labels = scales::dollar_format()) + 
  scale_y_continuous(labels = scales::comma_format()) + 
  labs(
    title = "Total Profit by the number of Units Sold",
    subtitle = "Online Sales earn the most profit",
    x = "Total Profit ($)",
    y = "Units Sold",
    color = "Item Type",
    shape = "Sales Channel"
  ) +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
plot1
```

# Models to see which Sales Channel has more profit than the other

Let's start by tackling a specific question before going onto our central/general question,
The below plot shows what the total profit would be between the years of 2010 and 2017.

## Plot for Online
```{r}
# Plot for Online
#| label: model1
#| message: false
#| warning: FALSE

plot2 <- fit_x2 |>
  add_epred_draws(newdata = ndata) |>
  filter(Sales_Channel == "Online") |>
  ggplot(aes(x = Order_Year, y = .epred)) +
  geom_point(color = "#FFC470", size = 3, alpha = 0.6) +  # Change point color and size
  geom_smooth(method = "gam", color = "#8B322C", se = FALSE, linewidth = 1, formula = y ~ x) +  # Smooth line customization
  labs(
    title = "Predicted Total Profit for Online Sales Channel",
    x = "Order Year",
    y = "Predicted Total Profit",
    caption = "Source: Kaggle, Amazon Sales Dataset"
  ) +
  scale_y_continuous(limits = c(-500000, 1000000), breaks = c(-500000, 0, 500000, 1000000)) +
  theme_classic(base_size = 15) +  # Minimal theme with larger base font size
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),  # Center and bold title
    plot.caption = element_text(size = 10, face = "italic"),  # Style caption
    axis.text = element_text(color = "black")  # Ensure axis text is clear
  )

plot2
```

### Explanation

This graph visualizes the predicted total profit for the "Online" sales channel over various order years. The orange points represent individual predictions, while the maroon smooth line, created using a generalized additive model (GAM), illustrates the overall trend. The y-axis, ranging from -500,000 to 1,000,000, captures both potential losses and profits. The spread of points around the smooth line indicates variability in predictions, with the line suggesting whether profits are expected to rise, fall, or show a more complex pattern over time.

## Plot for Offline

```{r}
# Plot for Offline
#| label: model2
#| message: false
#| warning: FALSE

plot3 <- fit_x2 |>
  add_epred_draws(newdata = ndata) |>
  filter(Sales_Channel == "Offline") |>
  filter(!is.na(.epred) & .epred >= 0 & .epred <= 800000) |>
  ggplot(aes(x = Order_Year, y = .epred)) +
  geom_point(color = "#729762", size = 3, alpha = 0.6) +  # Change point color and size
  geom_smooth(method = "gam", color = "#254336", se = FALSE, linewidth = 1, formula = y ~ x) +  # Smooth line customization
  labs(
    title = "Predicted Total Profit for Offline Sales Channel",
    x = "Order Year",
    y = "Predicted Total Profit",
    caption = "Source: Kaggle, Amazon Sales Dataset"
  ) +
  scale_y_continuous(limits = c(0, 800000)) +
  theme_classic(base_size = 15) +  # Classical theme 
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),  # Center and bold title
    plot.caption = element_text(size = 10, face = "italic"),  # Style caption
    axis.text = element_text(color = "black")  # Ensure axis text is clear
  )
plot3
```

### Explanation

This plot visualizes the predicted total profit for the "Offline" sales channel over various order years. Green points represent individual profit predictions, while a dark green smoothing line shows the overall trend using a generalized additive model (GAM). The y-axis, ranging from 0 to 800,000, highlights positive profits, with data filtered to exclude missing or extreme values. The plot, indicates how predicted profits for offline sales change over time, revealing both the trend and the variability in the model's predictions.
