---
title: "Visual Analysis"
execute: 
  echo: false
---
## Fitted Model

```{r}
#| message: false
#| label: setup
#| warning: false

library(tidybayes)
library(tidyverse)
library(brms)
library(plotly)
library(gtsummary)
```

```{r}
#| label: raw_data
#| warning: false
#| message: false
raw_df <- read_csv("data/AmazonSalesData.csv", show_col_types = FALSE)
```

```{r}
#| label: cleaning
#| message: false
#| warning: false
AmazonSales <- raw_df |>
  rename(`Manufacturing Cost` = `Unit Cost`,
         Total_Profit = `Total Profit`,
         Sales_Channel = `Sales Channel`) |>
  select(Sales_Channel, `Manufacturing Cost`, Total_Profit, `Order Priority`, `Order Date`) |> 
  mutate(`Order Priority` = recode(`Order Priority`,
                                   "H" = "High Priority",
                                   "C" = "Critical Priority",
                                   "L" = "Low Priority",
                                   "M" = "Medium Priority")) |>
  mutate(Order_Year = year(mdy(`Order Date`)))
```

```{r}
#| cache: true
#| message: false
#| label: brm_model
#| warning: false

fit_x2 <- brm(formula = Total_Profit ~ Order_Year + Sales_Channel,
              data = AmazonSales,
              family = gaussian(),
              silent = 2,
              refresh = 0,
              seed = 17)
```

```{r}
#| label: variable
#| message: false
#| warning: false

ndata = tibble("Order_Year" = c(2010:2027),
               "Sales_Channel" = rep(c("Online", "Offline"), times = 9))
```

```{r}
#| label: model3
#| message: false
#| warning: false

plot4 <- fit_x2 |>
  add_epred_draws(newdata = ndata) |>
  filter(Sales_Channel == "Online") |>
  ggplot(aes(x = Order_Year, y = .epred)) +
  geom_point(color = "#ECB159", size = 3, alpha = 0.6) +  # Change point color and size
  geom_smooth(method = "loess", color = "#B67352", se = FALSE, size = 1) +  # Smooth line customization
  labs(
    title = "Predicted Total Profit for Online Sales Channel",
    x = "Order Year",
    y = "Predicted Total Profit",
    caption = "Source: Kaggle, Amazon Sales Dataset"
  ) +
  theme_minimal(base_size = 15) +  # Minimal theme with larger base font size
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),  # Center and bold title
    plot.caption = element_text(size = 10, face = "italic"),  # Style caption
    axis.text = element_text(color = "black")  # Ensure axis text is clear
  )
plot4
```

```{r}
#| label: model4
#| message: false
#| warning: false

plot5 <- fit_x2 |>
  add_epred_draws(newdata = ndata) |>
  filter(Sales_Channel == "Offline") |>
  ggplot(aes(x = Order_Year, y = .epred)) +
  geom_point(color = "#A2678A", size = 3, alpha = 0.6) +  # Change point color and size
  geom_smooth(method = "loess", color = "#3F1D38", se = FALSE, size = 1) +  # Smooth line customization
  labs(
    title = "Predicted Total Profit for Offline Sales Channel",
    x = "Order Year",
    y = "Predicted Total Profit",
    caption = "Source: Kaggle, Amazon Sales Dataset"
  ) +
  theme_minimal(base_size = 15) +  # Minimal theme with larger base font size
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),  # Center and bold title
    plot.caption = element_text(size = 10, face = "italic"),  # Style caption
    axis.text = element_text(color = "black")  # Ensure axis text is clear
  )
plot5
```

## Central Question
This plot answers our general/central question which answers how the profit increasing trend would be during upcoming years.

```{r}
#| label: model5
#| message: false
#| warning: false

plot6 <- fit_x2 |>
  add_epred_draws(newdata = ndata) |>
  ggplot(aes(x = Order_Year, y = .epred)) +
  geom_point(color = "#03346E", size = 3, alpha = 0.6) +  # Change point color and size
  geom_smooth(method = "loess", color = "#6EACDA", se = FALSE, size = 1) +  # Smooth line customization
  labs(
    title = "Predicted Total Profit by Order Year",
    x = "Order Year",
    y = "Predicted Total Profit",
    caption = "Source: Kaggle, Amazon Sales Dataset"
  ) +
  theme_minimal(base_size = 15) +  # Minimal theme with larger base font size
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),  # Center and bold title
    plot.caption = element_text(size = 10, face = "italic"),  # Style caption
    axis.text = element_text(color = "black")  # Ensure axis text is clear
  )
plot6
```

## Graph Explanation
The plot visualizes the predictions from a Bayesian regression model where total profit is modeled as a function of order year using a Gaussian distribution. The blue points represent the model's predicted profits for each year from 2010 to 2026, while the red LOESS curve smooths these predictions to reveal the overall trend. The plot, with its clear axis labels, centered title, and styled caption, suggests how the model expects total profit to evolve over time, providing valuable insights into potential profit trends and helping guide future business decisions.
\n
\n
The inclusion of a LOESS curve in the plot adds a nuanced layer of analysis by highlighting potential non-linear patterns that a simple linear regression might overlook. This is particularly important in financial forecasting, where trends can fluctuate due to various external factors. The Bayesian framework further strengthens the model by incorporating prior information and providing a probabilistic interpretation of the predictions, which can help in assessing uncertainty and making more informed decisions. Together, these elements make the plot a powerful tool for visualizing and understanding the complex dynamics of profit trends over time, offering both immediate insights and a foundation for deeper analysis.


## Quantitative Analysis

```{r}
#| warning: false
# creates the regression table summarizing 
fit_x2 |>
  tbl_regression()
```

### Formula
$$
TotalProfit_i = \beta_0 + \beta_1SalesChannel + \beta_2OrderYear + \epsilon_i
$$

## Explanation of regression table
The regression results provide an insight into the relationship between the predictor variables—Order Year and Sales Channel—and the predicted Total Profit. The estimated coefficient (Beta) for Order Year is 764, with a 95% Credible Interval (CI) ranging from -39,321 to 42,843. This wide interval, which includes zero, suggests that the effect of Order Year on Total Profit is uncertain, indicating no clear evidence of a positive or negative trend over time.

For the Sales Channel variable, the category Online has an estimated coefficient of -114,969 with a 95% CI of -294,935 to 58,348. This suggests that, on average, online sales may be associated with a decrease in Total Profit compared to the baseline (likely offline or another sales channel), but the large interval again includes zero, indicating considerable uncertainty. 
## Posterior Perdictive Check

```{r}
fit_x2 |>
  pp_check()
```
